### 2019-09-11 reports/thesis/chapters/2_dataCollection.tex
Use proofreader

Many figures presented here were given by engineers in relation to the experiment or by the manufacturer. Figures with no error bars were rounded to an appropriate number of significant figures.

@@

\emph{aRTist} was used to simulate the test object projection and all greyscale projections except for the black image. The black image was simulated by producing an uniform image with grey value the mean over the obtained black image. The engineers used numerical methods to align the simulated projection with the obtained projection.

@@

The projections show the test sample, but, with panel and spot effects. The structure of the 32 panels are predominate in the black image in particular, this was observed by \cite{yang2009evaluation} as well. This is concerning because systematic errors could be introduced as a result of the panel effects in the black image. This should not happen because in a black image, the detector is exposed only to background radiation. The x-ray spot can be observed, in particular, in the white image, and this is the result of using a cone beam.

@@

In this section, the shading correction in \cite{seibert1998flat} is presented in a form without any user defined constants. The shading correction was experimented to investigate its performance when shading correcting greyscale projections.

@@

A variation of the shading correction which uses only the black and white image such that $\mathbb{P}=\left\{0,P_\text{proj}\right\}$ shall be known as black/white (BW) shading correction.

@@

It was investigated if shading correction on a greyscale projection result in an image which is flat with some noise. To avoid overfitting, one greyscale projection from each power was held out and used to fit the parameters of the shading correction. Shading correction was then used on the unused greyscale projections in this exploratory analysis.

@@

An experiment was conducted to quantify the performance of the different types of shading correction. Applying shading correction on the greyscale image should remove effects from the panels and the spot, leaving a flat noisy image with no spatial structure. The variance within a pixel and across replications should be similar to the variance between pixels within a replication if shading correction flatten the greyscale images.

In each dataset, there are 20 replicated greyscale images for each power. One randomly selected replication from each power was assigned to the training set and used to calibrate the shading correction. The remaining images was assigned to the test set and the shading correction was applied to each image.

@@

The results are shown in Figures \ref{fig:data_anovaAbsNoFilter} and \ref{fig:data_anovaAbsFilter} for the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter} respectively. With shading correction, the within and between pixel variance became more similar. A difference between BW and linear shading correction was that for the black image, the $F$ statistic is closer to one for BW shading correction compared to linear shading correction. For the rest of the powers, linear shading correction outperformed BW shading correction. This shows that linear shading correction generalise to powers between zero and $P_\text{proj}$. Since beam extinction is avoided, black grey values in the obtained projection should not be possible. As a result, the linear shading correction is recommended for its good performance for various powers.

Using the $F$ test from ANOVA was found to be too strict in this experiment. Under the hypothesis that the grey values all have the same mean and assume they are Normally distributed and i.i.d., then $F(P)\sim F_{WH-1,WH(n-1)}$. In this experiment, the 5\% critical value is 1.001 to 3 decimal places, this is too small for the purpose of this analysis. This may be due to the grey values of the greyscale projections not satisfying the assumptions for the $F$ test, for example they may not be i.i.d.

@@

Shading correction is important because it removes any panel and spot effects from projections which may cause systematic errors in any statistical analysis. Shading correcting the greyscale projections visually produced a flat image but there were some spatial variation which was picked up by the between pixel variances in ANOVA.

@@

The variance of the greyscale projections were studied in this chapter. This is straightforward because the greyscale projections are flat images. The noise of a projection of a test sample is studied in the next chapter and this was done by modelling the grey value of each pixel as a compound Poisson random variable.

>>>>

Many figures presented here were given by engineers concerning the experiment or by the manufacturer. Figures with no error bars were rounded to an appropriate number of significant figures.

@@

\emph{aRTist} was used to simulate the test object projection and all greyscale projections except for the black image. The black image was simulated by producing a uniform image with a grey value the mean over the obtained black image. The engineers used numerical methods to align the simulated projection with the obtained projection.

@@

The projections show the test sample, but, with panel and spot effects. The structure of the 32 panels are predominate in the black image, in particular, this was observed by \cite{yang2009evaluation} as well. This is concerning because systematic errors could be introduced as a result of the panel effects in the black image. This should not happen because, in a black image, the detector is exposed only to background radiation. The x-ray spot can be observed, in particular, in the white image, and this is the result of using a cone beam.

@@

In this section, the shading correction in \cite{seibert1998flat} is presented in a form without any user-defined constants. The shading correction was experimented to investigate its performance when shading correcting greyscale projections.

@@

A variation of the shading correction which uses only the black and white image such that $\mathbb{P}=\left\{0, P_\text{proj}\right\}$ shall be known as black/white (BW) shading correction.

@@

It was investigated if shading correction on a greyscale projection results in an image which is flat with some noise. To avoid overfitting, one greyscale projection from each power was held out and used to fit the parameters of the shading correction. Shading correction was then used on the unused greyscale projections in this exploratory analysis.

@@

An experiment was conducted to quantify the performance of the different types of shading correction. Applying shading correction on the greyscale image should remove effects from the panels and the spot, leaving a flat noisy image with no spatial structure. The variance within a pixel and across replications should be similar to the variance between pixels within a replication if shading correction flattens the greyscale images.

In each dataset, there are 20 replicated greyscale images for each power. One randomly selected replication from each power was assigned to the training set and used to calibrate the shading correction. The remaining images were assigned to the test set and the shading correction was applied to each image.

@@

The results are shown in Figures \ref{fig:data_anovaAbsNoFilter} and \ref{fig:data_anovaAbsFilter} for the datasets \texttt{AbsNoFilter} and \texttt{AbsFilter} respectively. With shading correction, the within and between pixel variance became more similar. A difference between BW and linear shading correction was that for the black image, the $F$ statistic is closer to one for BW shading correction compared to linear shading correction. For the rest of the powers, linear shading correction outperformed BW shading correction. This shows that linear shading correction generalises to powers between zero and $P_\text{proj}$. Since beam extinction is avoided, black grey values in the obtained projection should not be possible. As a result, the linear shading correction is recommended for its good performance for various powers.

Using the $F$ test from ANOVA was found to be too strict in this experiment. Under the hypothesis that the grey values all have the same mean and assume they are Normally distributed and i.i.d., then $F(P)\sim F_{WH-1, WH(n-1)}$. In this experiment, the 5\% critical value is 1.001 to 3 decimal places, this is too small for this analysis. This may be due to the grey values of the greyscale projections not satisfying the assumptions for the $F$ test, for example, they may not be i.i.d.

@@

Shading correction is important because it removes any panel and spot effects from projections which may cause systematic errors in any statistical analysis. Shading correcting the greyscale projections visually produced a flat image but there was some spatial variation which was picked up by the between pixel variances in ANOVA.

@@

The variance of the greyscale projections was studied in this chapter. This is straightforward because the greyscale projections are flat images. The noise of a projection of a test sample is studied in the next chapter and this was done by modelling the grey value of each pixel as a compound Poisson random variable.
